\chapter{Implementation}

This chapter will cover the actual implementation of the project. The whole process of implementation was split into two parts: creation of the MPI Layer and clustering implementation within the Mapper class.

\section{MPI Layer}

The MPI Layer, as mentioned before, operates, based on the two main entities - \textbf{MasterSimulation} and \textbf{WorkerSimulation} classes.

\emph{MasterSimulation} is responsible for clustering and separation of the user input, distribution of this information to the corresponding workers and synchronisation of workers during simulation timesteps. It is the core class of the simulation, as it receives original network parameters, specified by the user.

\emph{WorkerSimulation} (sometimes regarded as nodes) is running the simulation and communicates with Master, to receive user-input information (initialisation parameters), and with other Workers during simulation. This is an auxiliary class, that is fully responsible for the local NeMo simulation running on its cluster.

\subsection{Basic Distributed Platform}

The construction of the basic platform focused on establishing the communication channel between the master simulation and the worker ones. 

\subsubsection{Initial parameters distribution}

Initial solution - basic platform + ditribution of parameters implementation

\subsection{Communication Channels Integration}

Communication scheme implementation

\subsubsection{Spike Enqueing}

Spike delivery - enqueing and updates

\subsubsection{Spike Distribution}

Spikes - firing and distribution

\section{Clustering}

Mapping algorithm implementation

\subsection{Newman's Algorithm}

Newman's work in detail

\subsection{Mapper integration}

His algorithm implemented with code snippets

\section{Alternative Solutions}

\begin{itemize}
\item{Use of Boost libraries}
\end{itemize}
