\documentclass[12pt]{report}
  \title{\LARGE Distributed Simulation of Spiking Neural Networks using Message Passing Interface \\ \vspace{7mm} \large Final Year Project}
  \author{ \emph{Author:} \\ Iskander Orazbekov \vspace{5 mm} \\ \emph{Supervisor:} \\ Dr Timothy Todman \vspace{5 mm} \\ \emph{Second Marker:} \\ Professor Murray Shanahan \vspace{56 mm} \\ Imperial College London}
  \date{\today}
\usepackage{a4}
\usepackage{listings}
\lstset{
	language=C++,
	frame=single,
	numbers=left,
	breaklines=true,
	breakautoindent=true,
	xleftmargin={\ifodd\value{page}1em\else-\marginparwidth\fi},
	xrightmargin={\ifodd\value{page}-\marginparwidth\else1em\fi},
	basicstyle=\ttfamily\footnotesize\bfseries,
	frame=tb
}
\usepackage{graphicx}
\usepackage{url}
\usepackage[english]{babel}
\usepackage{wrapfig}
\usepackage[toc,page]{appendix}
\setlength{\parskip}{0.3cm}
\setlength{\parindent}{0cm}

\begin{document}

\maketitle

\begin{abstract}

Motivation behind the development of spiking neural networks arised from the growing interest in the area of neural 
computation and studies of brain activity in the recent years. The reason lies in the fact that SNNs incorporate time
into neuron firing computation and signify the role of interconnectedness between neurons, therefore bringing the simulation 
level closer to reality.

However, as a result of such improvement, spiking neural networks are computationally expensive to simulate, therefore, a solution 
using parallel computation was needed. NeMo, a Spiking Neural Network simulator developed at Imperial College, solves this problem 
by making use of CUDA-interfaced GPUs with high level of parallelism.

The aim of this project is to implement the Message Passing Interface for NeMo, and by doing this, improve inter-neural communication, 
to allow for better performance of parallel computations. This, in turn, will allow for bigger number of neurons within the network 
and greater level of realism brought by the simulation.

\end{abstract}

\clearpage

\chapter*{Acknowledgements}
\thispagestyle{empty}

I would like to thank Dr Timothy Todman for his guidance throughout the project and his sense of reason that helped me structure it. I would also like to thank Dr Andreas Fidjeland for his enthusiasm that sparkled my interest in this project and technical guidance that did not let me get lost at the start. I would like to thank Professor Murray Shanahan for his mathematical knowledge that helped me with clustering integration. On a separate note, I would like to thank Matthias Hueser for his technical expertise and advices.
I would also like to thank my parents for their moral support and guidance throughout this project.


\clearpage

\tableofcontents

\renewcommand{\chaptername}{}

\input{1_introduction}

\input{2_background}

\input{3_design}

\input{4_implementation}

\input{5_evaluation}

\input{6_conclusion}

\clearpage

\bibliographystyle{plain}
\bibliography{myrefs}

\begin{appendices}

\chapter{Simulation Classes}
\section{MasterSimulation}
\lstinputlisting{code/MasterSimulation.hpp}
\clearpage
%This page is intentionally left blank
\lstinputlisting{code/MasterSimulation.cpp}
\clearpage
\section{WorkerSimulation}
\lstinputlisting{code/WorkerSimulation.hpp}
\clearpage
%This page is intentionally left blank
\lstinputlisting{code/WorkerSimulation.cpp}
\clearpage
\chapter{Full Mapper Implementation}
\lstinputlisting{code/MapperSim.hpp}
\clearpage
%This page is intentionally left blank
\lstinputlisting{code/MapperSim.cpp}
\clearpage

\end{appendices}

\end{document}
